---
title: "Project2"
output: html_notebook
---
# Import Libraries
```{r}
library(tidyverse)
library(rvest)
library(tibble)
```

# Test Scrape
```{r}
# url <- "https://www.maxpreps.com/nc/baseball/23-24/division/class-4a-east/scores/?date=2/21/2024&statedivisionid=a7f97dc1-38dc-43de-b089-26126494000a"
# html <- read_html(url)
# 
# 
# html %>% html_elements("div.contest-box-item") %>% html_text2()
```

# Test Scrape (Multiple Games)
```{r}
# url <- "https://www.maxpreps.com/nc/baseball/23-24/division/class-4a-east/scores/?date=2/26/2024&statedivisionid=a7f97dc1-38dc-43de-b089-26126494000a"
# html <- read_html(url)
# 
# 
# games_d1 <- html %>% html_elements("div.contest-box-item") %>% html_text2()
# games_d1_df <- as_tibble(games_d1)
```

# Clean data
```{r}
# class(games_d1)
# data <- games_d1[!duplicated(games_d1) | games_d1 != "\r"]
# 
# # Split the data into separate columns based on \r
# split_data <- strsplit(data, "\r")
# 
# # Remove empty strings
# split_data <- lapply(split_data, function(x) x[x != ""])
# 
# # Determine the maximum number of games in any row
# max_games <- max(lengths(split_data))
# 
# # Pad shorter rows with NA values
# split_data <- lapply(split_data, function(x) c(x, rep(NA, max_games - length(x))))
# 
# # Convert to data frame
# df <- as.data.frame(do.call(rbind, split_data))
# 
# # Rename columns
# colnames(df) <- paste0("col_", 1:max_games)
# 
# # Print the resulting data frame
# print(df)
```


# Keep games I want
```{r}
# target_section_found <- FALSE
# 
# # Initialize a list to store the games you want to keep
# games_to_keep <- list()
# 
# # Iterate through each row of the data frame
# target_section_found <- FALSE
# 
# # Initialize a list to store the games you want to keep
# games_to_keep <- list()
# 
# # Iterate through each row of the data frame
# for (i in 1:nrow(df)) {
#     # Check if the row belongs to the target section
#     if (!target_section_found) {
#         # Check your condition for identifying the target section
#         if (!is.na(df[i, 1])) {
#             target_section_found <- TRUE
#             games_to_keep <- rbind(games_to_keep, df[i, ])
#         }
#     } else {
#         # Check if the row is a blank row
#         if (all(is.na(df[i, ]))) {
#             # Exit the loop if a blank row is encountered after the target                section
#             break
#         } else {
#             # Keep adding games to the list if they are within the target                 section
#             games_to_keep <- rbind(games_to_keep, df[i, ])
#         }
#     }
# }
# 
# # Convert the list of games to keep back to a data frame
# df_filtered <- as.data.frame(games_to_keep)
# print(df_filtered)
```

# Reformat dataframe
```{r}
# df_filtered <- df_filtered[, c(1, 2, 5, 6)]
# print(df_filtered)
# 
# 
# # Rename columns
# colnames(df_filtered)[1] <- "away_score"
# colnames(df_filtered)[2] <- "away_team"
# colnames(df_filtered)[3] <- "home_score"
# colnames(df_filtered)[4] <- "home_team"
# print(df_filtered)
# 
# # Reorder columns
# df_filtered <- df_filtered[, c(4,3, 2, 1 )]
# 
# df_filtered$away_team <- gsub("\\s*\\(#[0-9]+\\)\\s*", "", df_filtered$away_team)
# df_filtered$home_team <- gsub("\\s*\\(#[0-9]+\\)\\s*", "", df_filtered$home_team)
# # Print the resulting data frame
# print(df_filtered)

```

# Trying some looping techniques 
## Hoping to start by getting the games from February and we'll go from there
```{r}
game_data = NULL
range <- 26:29
days <- c(21, range)
feb_game_data = NULL
base_url <- "https://www.maxpreps.com/nc/baseball/23-24/division/class-4a-east/scores/?date=2/dd/2024&statedivisionid=a7f97dc1-38dc-43de-b089-26126494000a"
day_placeholder <- "dd"
for (day in days) {
  # REPLACE DAYS
  url <- gsub(day_placeholder, substr(day, 1, 2), base_url)
  #print(url)
  
  # PERFORM SCRAPE
  html <- read_html(url)
  games_dummy <- html %>% html_elements("div.contest-box-item") %>%   html_text2()
  games_dummy_df <- as_tibble(games_dummy)
  
  # CLEAN DATA
  data <- games_dummy[!duplicated(games_dummy) | games_dummy != "\r"]
  ## Split the data into separate columns based on \r
  split_data <- strsplit(data, "\r")
  ## Remove empty strings
  split_data <- lapply(split_data, function(x) x[x != ""])
  ## Determine the maximum number of games in any row
  max_games <- max(lengths(split_data))
  ## Pad shorter rows with NA values
  split_data <- lapply(split_data, function(x) c(x, rep(NA, max_games - length(x))))
  ## Convert to data frame
  df <- as.data.frame(do.call(rbind, split_data))
  ## Rename columns
  colnames(df) <- paste0("col_", 1:max_games)
  
  # REMOVE EXCESS GAMES
  target_section_found <- FALSE
  # Initialize a list to store the games you want to keep
  games_to_keep <- list()
  # Iterate through each row of the data frame
  target_section_found <- FALSE
  # Initialize a list to store the games you want to keep
  games_to_keep <- list()
  # Iterate through each row of the data frame
  for (i in 1:nrow(df)) {
      # Check if the row belongs to the target section
      if (!target_section_found) {
          # Check your condition for identifying the target section
          if (!is.na(df[i, 1])) {
              target_section_found <- TRUE
              games_to_keep <- rbind(games_to_keep, df[i, ])
          }
      } else {
          # Check if the row is a blank row
          if (all(is.na(df[i, ]))) {
              # Exit the loop if a blank row is encountered after the target                section
              break
          } else {
              # Keep adding games to the list if they are within the target                 section
              games_to_keep <- rbind(games_to_keep, df[i, ])
          }
      }
  }
  # Convert the list of games to keep back to a data frame
  df_filtered <- as.data.frame(games_to_keep)
  
  # REFORMAT DATA
  df_filtered <- df_filtered[, c(1, 2, 5, 6)]
  # Rename columns
  colnames(df_filtered)[1] <- "away_score"
  colnames(df_filtered)[2] <- "away_team"
  colnames(df_filtered)[3] <- "home_score"
  colnames(df_filtered)[4] <- "home_team"
  # Reorder columns
  df_filtered <- df_filtered[, c(4,3, 2, 1 )]
  df_filtered$away_team <- gsub("\\s*\\(#[0-9]+\\)\\s*", " ", df_filtered$away_team)
  df_filtered$home_team <- gsub("\\s*\\(#[0-9]+\\)\\s*", " ", df_filtered$home_team)
  df_filtered$game_date <- paste0("2/",day,"/24")

  #print(df_filtered)
  feb_game_data <- rbind(feb_game_data,df_filtered)
}
```

# March data
## I know this isn't the most efficient way, and I will clean this up (hopefully), but I'm going to scrape each month individually and then bind them together

```{r}

range <- 1:31
items_to_remove <- c(2,3,6,9,10,17,24,31)

# Remove specific items from the list
days <- range[!range %in% items_to_remove]

mar_game_data = NULL
base_url <- "https://www.maxpreps.com/nc/baseball/23-24/division/class-4a-east/scores/?date=3/dd/2024&statedivisionid=a7f97dc1-38dc-43de-b089-26126494000a"
day_placeholder <- "dd"
for (day in days) {
  # REPLACE DAYS
  url <- gsub(day_placeholder, substr(day, 1, 2), base_url)
  #print(url)
 
  # PERFORM SCRAPE
  html <- read_html(url)
  games_dummy <- html %>% html_elements("div.contest-box-item") %>%   html_text2()
  games_dummy_df <- as_tibble(games_dummy)
  
  # CLEAN DATA
  data <- games_dummy[!duplicated(games_dummy) | games_dummy != "\r"]
  ## Split the data into separate columns based on \r
  split_data <- strsplit(data, "\r")
  ## Remove empty strings
  split_data <- lapply(split_data, function(x) x[x != ""])
  ## Determine the maximum number of games in any row
  max_games <- max(lengths(split_data))
  ## Pad shorter rows with NA values
  split_data <- lapply(split_data, function(x) c(x, rep(NA, max_games - length(x))))
  ## Convert to data frame
  df <- as.data.frame(do.call(rbind, split_data))
  ## Rename columns
  colnames(df) <- paste0("col_", 1:max_games)
  
  # REMOVE EXCESS GAMES
  target_section_found <- FALSE
  # Initialize a list to store the games you want to keep
  games_to_keep <- list()
  # Iterate through each row of the data frame
  target_section_found <- FALSE
  # Initialize a list to store the games you want to keep
  games_to_keep <- list()
  # Iterate through each row of the data frame
  for (i in 1:nrow(df)) {
      # Check if the row belongs to the target section
      if (!target_section_found) {
          # Check your condition for identifying the target section
          if (!is.na(df[i, 1])) {
              target_section_found <- TRUE
              games_to_keep <- rbind(games_to_keep, df[i, ])
          }
      } else {
          # Check if the row is a blank row
          if (all(is.na(df[i, ]))) {
              # Exit the loop if a blank row is encountered after the target                section
              break
          } else {
              # Keep adding games to the list if they are within the target                 section
              games_to_keep <- rbind(games_to_keep, df[i, ])
          }
      }
  }
  # Convert the list of games to keep back to a data frame
  df_filtered <- as.data.frame(games_to_keep)
  
  # REFORMAT DATA
  df_filtered <- df_filtered[, c(1, 2, 5, 6)]
  # Rename columns
  colnames(df_filtered)[1] <- "away_score"
  colnames(df_filtered)[2] <- "away_team"
  colnames(df_filtered)[3] <- "home_score"
  colnames(df_filtered)[4] <- "home_team"
  # Reorder columns
  df_filtered <- df_filtered[, c(4,3, 2, 1 )]
  df_filtered$away_team <- gsub("\\s*\\(#[0-9]+\\)\\s*", " ", df_filtered$away_team)
  df_filtered$home_team <- gsub("\\s*\\(#[0-9]+\\)\\s*", " ", df_filtered$home_team)
  df_filtered$game_date <- paste0("3/",day,"/24")

  # print_filtered
  mar_game_data <- rbind(mar_game_data,df_filtered)
}
```



# April data
## I know this isn't the most efficient way, and I will clean this up (hopefully), but I'm going to scrape each month individually and then bind them together
```{r}

range <- 1:22
items_to_remove <- c(7,14,21)


# Remove specific items from the list
days <- range[!range %in% items_to_remove]

apr_game_data = NULL
base_url <- "https://www.maxpreps.com/nc/baseball/23-24/division/class-4a-east/scores/?date=4/dd/2024&statedivisionid=a7f97dc1-38dc-43de-b089-26126494000a"
day_placeholder <- "dd"
for (day in days) {
  # REPLACE DAYS
  url <- gsub(day_placeholder, substr(day, 1, 2), base_url)
  #print(url)
 
  # PERFORM SCRAPE
  html <- read_html(url)
  games_dummy <- html %>% html_elements("div.contest-box-item") %>%   html_text2()
  games_dummy_df <- as_tibble(games_dummy)
  
  # CLEAN DATA
  data <- games_dummy[!duplicated(games_dummy) | games_dummy != "\r"]
  ## Split the data into separate columns based on \r
  split_data <- strsplit(data, "\r")
  ## Remove empty strings
  split_data <- lapply(split_data, function(x) x[x != ""])
  ## Determine the maximum number of games in any row
  max_games <- max(lengths(split_data))
  ## Pad shorter rows with NA values
  split_data <- lapply(split_data, function(x) c(x, rep(NA, max_games - length(x))))
  ## Convert to data frame
  df <- as.data.frame(do.call(rbind, split_data))
  ## Rename columns
  colnames(df) <- paste0("col_", 1:max_games)
  
  # REMOVE EXCESS GAMES
  target_section_found <- FALSE
  # Initialize a list to store the games you want to keep
  games_to_keep <- list()
  # Iterate through each row of the data frame
  target_section_found <- FALSE
  # Initialize a list to store the games you want to keep
  games_to_keep <- list()
  # Iterate through each row of the data frame
  for (i in 1:nrow(df)) {
      # Check if the row belongs to the target section
      if (!target_section_found) {
          # Check your condition for identifying the target section
          if (!is.na(df[i, 1])) {
              target_section_found <- TRUE
              games_to_keep <- rbind(games_to_keep, df[i, ])
          }
      } else {
          # Check if the row is a blank row
          if (all(is.na(df[i, ]))) {
              # Exit the loop if a blank row is encountered after the target                section
              break
          } else {
              # Keep adding games to the list if they are within the target                 section
              games_to_keep <- rbind(games_to_keep, df[i, ])
          }
      }
  }
  # Convert the list of games to keep back to a data frame
  df_filtered <- as.data.frame(games_to_keep)
  
  # REFORMAT DATA
  df_filtered <- df_filtered[, c(1, 2, 5, 6)]
  # Rename columns
  colnames(df_filtered)[1] <- "away_score"
  colnames(df_filtered)[2] <- "away_team"
  colnames(df_filtered)[3] <- "home_score"
  colnames(df_filtered)[4] <- "home_team"
  # Reorder columns
  df_filtered <- df_filtered[, c(4,3, 2, 1 )]
  df_filtered$away_team <- gsub("\\s*\\(#[0-9]+\\)\\s*", " ", df_filtered$away_team)
  df_filtered$home_team <- gsub("\\s*\\(#[0-9]+\\)\\s*", " ", df_filtered$home_team)
  df_filtered$game_date <- paste0("4/",day,"/24")

  #print(df_filtered)
  apr_game_data <- rbind(apr_game_data,df_filtered)
}
```




# Merge Feb/Mar game data together
```{r}
game_data <- rbind(feb_game_data,mar_game_data)
game_data <- rbind(game_data,apr_game_data)
game_data <- game_data[game_data$home_team != "\n", ]
game_data <- game_data[game_data$home_team != " ", ]
game_data$away_score <- ifelse(is.na(game_data$away_score), 0, game_data$away_score)

game_data$home_score <- as.numeric(game_data$home_score)
game_data$away_score <- as.numeric(game_data$away_score)
game_data$game_result <- ifelse(game_data$home_score > game_data$away_score, 1, 0)
game_data$home_rating <- 1500
game_data$away_rating <- 1500
game_data$game_id <- seq(1, nrow(game_data))

game_data %>% filter(is.na(home_score)|is.na(away_score)) %>% arrange(game_date)

```

# Elo calculations
```{r}
prob_win <- function(team_rating, opp_team_rating, divisor = 600){
  return(1 / (1 + 10^((opp_team_rating - team_rating) / divisor)))
}

# calculates the updated elo rating for a team based on the teams
calc_new_rating <- function(team_rating, game_result, prob_win, k_factor = 40){
  return(team_rating + k_factor * (game_result - prob_win))
}
```


# Group by team
```{r}
elo_data <- game_data
for(i in 1:nrow(elo_data)){
  # select the game id for the current game (used for indexing)
  game_id = elo_data$game_id[i]
  
  # select the teams that play in game i
  home_team = elo_data$home_team[i]
  away_team = elo_data$away_team[i]
  
  # select the teams elo going into game i
 home_team_elo = elo_data$home_rating[i]
  away_team_elo = elo_data$away_rating[i]

  # # outcome of game i
  outcome = elo_data$game_result[i]
  # # calculate the probability of winning based on current elo
  prob1wins = prob_win(home_team_elo, away_team_elo)
  prob2wins = prob_win(away_team_elo, home_team_elo)
  
  # # calculate the new elo rating for each team
  new_rating_team1 = calc_new_rating(home_team_elo, outcome, prob1wins)
  new_rating_team2 = calc_new_rating(away_team_elo, 1-outcome, prob2wins)
  
  #### update the new values in the data frame
  home_team_ind = (1:nrow(elo_data))[((elo_data$home_team == home_team) | (elo_data$away_team == home_team)) & (elo_data$game_id > game_id)][1]
  away_team_ind = (1:nrow(elo_data))[((elo_data$home_team == away_team) | (elo_data$away_team == away_team)) & (elo_data$game_id > game_id)][1]
  # # update team 1 elo
  if(!is.na(home_team_ind)){
    if(elo_data$home_team[home_team_ind] == home_team){
      elo_data$home_rating[home_team_ind] = new_rating_team1 # update
    }else{
      elo_data$away_rating[home_team_ind] = new_rating_team1 # update
    }
  }
  # update team 2 elo
  if(!is.na(away_team_ind)){
    if(elo_data$away_team[away_team_ind] == away_team){
      elo_data$away_rating[away_team_ind] = new_rating_team2
    }else{
      elo_data$home_rating[away_team_ind] = new_rating_team2
    }
  }
}
```

# Grouping data
```{r}
elo_plot = elo_data %>%
  pivot_longer(home_rating:away_rating, names_to = 'Group', values_to = 'ELO') %>%
  mutate(team = ifelse(Group == 'home_rating', home_team, away_team)) %>%
  select(game_date, ELO, team)
```

# Data exploration
```{r}
gh <- elo_plot %>% filter(team==" Green Hope")
apex <- elo_plot %>% filter(team==" Apex")

gh$game_date <- strptime(gh$game_date, format = "%m/%d/%y")
start_date <- as.POSIXlt("2024-02-21")

gh$season_day <- as.numeric(gh$game_date - start_date) + 1

ggplot(gh, aes(x = season_day, y = ELO)) +
  geom_line()
```

# Add season_day for all games
```{r}
elo_plot$game_date <- strptime(elo_plot$game_date, format = "%m/%d/%y")
start_date <- as.POSIXlt("2024-02-21")

elo_plot$season_day <- as.numeric(difftime(elo_plot$game_date, start_date, units = "days")) + 1
swac_teams <- c(" Green Hope", " Green Level", " Panther Creek", " Middle Creek", " Holly Springs", " Apex", " Apex Friendship", " Cary")

team_colors <- c(" Green Hope"="Dark Green", " Green Level"="Navy", " Panther Creek"="Sky Blue", " Middle Creek"="Black", " Holly Springs"="Purple", " Apex"="Yellow", " Apex Friendship"="Red", " Cary"="Lime Green")  # Add colors for each team


swac_data <- subset(elo_plot, team %in% swac_teams)
ggplot(swac_data, aes(x = season_day, y = ELO,color = team)) +
  geom_line() +scale_color_manual(values = team_colors)

```

# Conference coding
```{r}
#teams <- unique(c(elo_plot$team))
#teams
swac_teams <- c(" Green Hope", " Green Level", " Panther Creek", " Middle Creek", " Holly Springs", " Apex", " Apex Friendship", " Cary")
big_carolina_teams <- c(" D.H. Conley"," New Bern")
big_carolina_3a <- c(" Havelock", " Jacksonville", " J.H. Rose", " Northside - Jacksonville", " South Central")
mid_eastern_teams <- c(" Ashley"," Hoggard", " Laney", " New Hanover", " Topsail")
mid_eastern_3a <- c(" North Brunswick", " South Brunswick", " West Brunswick")
cap_six <- c(" Athens Drive", " Broughton", " Cardinal Gibbons", " Enloe", " Leesville Road", " Sanderson")
northern_athletic <- c(" Heritage", " Knightdale", " Millbrook", " Rolesville", " Wake Forest", " Wakefield")
united_eight <- c(" Jack Britt", " Gray's Creek", " Lumberton", " South View", " Purnell Swett")
united_eight_3a <- c(" Douglas Byrd", " Cape Fear", " Seventy-First")
greater_neuse <- c(" Corinth Holders", " Clayton", " Cleveland", " Fuquay - Varina", " Garner", " South Garner", " Southeast Raleigh", " Willow Spring")
dc_six <- c(" Jordan", " Chapel Hill", " East Chapel Hill", " Hillside", " Riverside-Durham", " Riverside-Durham")
all_american <- c(" Overhills", " Pine Forest")
all_american_3a <- c(" E.E. Smith", " Harnett Central", " Terry Sanford", " Triton", " Western Harnett", " Westover")
sandhills <- c(" Hoke County", " Pinecrest", " Richmond")
sandhills_3a <- c(" Lee County", " Scotland", " Southern Lee", " Union Pines")
metro <- c(" Grimsley", " Northern Guilford", " Northwest Guilford", " Page", " Ragsdale", " Southeast Guilford", " Southwest Guilford", " Western Guilford")
central_piedmont <- c(" Davie County", " East Forsyth", " Glenn", " Mount Tabor", " Parkland", " Reagan", " RJ Reynolds", " West Forsyth")

get_conference <- function(team) {
  if (team %in% swac_teams) {
    return("SWAC")
  } else if (team %in% big_carolina_teams) {
    return("Big Carolina")
  } else if (team %in% big_carolina_3a) {
    return("Big Carolina (3A)")
  }else if (team %in% mid_eastern_teams) {
    return("Mid Eastern")
  }else if (team %in% mid_eastern_3a) {
    return("Mid Eastern (3A)")
  }else if (team %in% cap_six) {
    return("CAP 6")
  }else if (team %in% northern_athletic) {
    return("Northern Athletic")
  }else if (team %in% united_eight) {
    return("United 8")
  }else if (team %in% united_eight_3a) {
    return("United 8 (3A)")
  }else if (team %in% greater_neuse) {
    return("Greater Neuse")
  }else if (team %in% dc_six) {
    return("DC 6")
  }else if (team %in% all_american) {
    return("All American")
  }else if (team %in% all_american_3a) {
    return("All American (3A)")
  }else if (team %in% sandhills) {
    return("Sandhills")
  }else if (team %in% sandhills_3a) {
    return("Sandhills (3A)")
  }else if (team %in% metro) {
    return("Metro")
  }else if (team %in% central_piedmont) {
    return("Central Piedmont")
  }  else {
    return("Other")
  }
}

# Apply function to create conference column
elo_plot$conference <- sapply(elo_plot$team, get_conference)

table(elo_plot$conference)
```
# A few other conference plots
```{r}
cap6_data <- subset(elo_plot, team %in% cap_six)
ggplot(cap6_data, aes(x = season_day, y = ELO,color = team)) +
  geom_line()

dc6_data <- subset(elo_plot, team %in% dc_six)
ggplot(dc6_data, aes(x = season_day, y = ELO,color = team)) +
  geom_line()
```



# Future Games (Hopefully to do some end of season projections and whatnot)
```{r}
today <- Sys.Date()
today_day <- format(today, "%d")
tomorrow_day <- as.numeric(today_day) + 2
range <- tomorrow_day:30
items_to_remove <- c(21,28)

# Remove specific items from the list
days <- range[!range %in% items_to_remove]

apr_future_game_data = NULL
base_url <- "https://www.maxpreps.com/nc/baseball/23-24/division/class-4a-east/scores/?date=4/dd/2024&statedivisionid=a7f97dc1-38dc-43de-b089-26126494000a"
day_placeholder <- "dd"
for (day in days) {
  # REPLACE DAYS
  url <- gsub(day_placeholder, substr(day, 1, 2), base_url)
  #print(url)

  # PERFORM SCRAPE
  html <- read_html(url)
  games_dummy <- html %>% html_elements("div.contest-box-item") %>%   html_text2()
  games_dummy_df <- as_tibble(games_dummy)

  # CLEAN DATA
  data <- games_dummy[!duplicated(games_dummy) | games_dummy != "\r"]
  ## Split the data into separate columns based on \r
  split_data <- strsplit(data, "\r")
  ## Remove empty strings
  split_data <- lapply(split_data, function(x) x[x != ""])
  ## Determine the maximum number of games in any row
  max_games <- max(lengths(split_data))
  ## Pad shorter rows with NA values
  split_data <- lapply(split_data, function(x) c(x, rep(NA, max_games - length(x))))
  ## Convert to data frame
  df <- as.data.frame(do.call(rbind, split_data))
  ## Rename columns
  colnames(df) <- paste0("col_", 1:max_games)

  # REMOVE EXCESS GAMES
  target_section_found <- FALSE
  # Initialize a list to store the games you want to keep
  games_to_keep <- list()
  # Iterate through each row of the data frame
  target_section_found <- FALSE
  # Initialize a list to store the games you want to keep
  games_to_keep <- list()
  # Iterate through each row of the data frame
  for (i in 1:nrow(df)) {
      # Check if the row belongs to the target section
      if (!target_section_found) {
          # Check your condition for identifying the target section
          if (!is.na(df[i, 1])) {
              target_section_found <- TRUE
              games_to_keep <- rbind(games_to_keep, df[i, ])
          }
      } else {
          # Check if the row is a blank row
          if (all(is.na(df[i, ]))) {
              # Exit the loop if a blank row is encountered after the target                section
              break
          } else {
              # Keep adding games to the list if they are within the target                 section
              games_to_keep <- rbind(games_to_keep, df[i, ])
          }
      }
  }
  # Convert the list of games to keep back to a data frame
  df_filtered <- as.data.frame(games_to_keep)

  # REFORMAT DATA
  df_filtered <- df_filtered[, c(1, 2, 5, 6)]
  # Rename columns
  colnames(df_filtered)[1] <- "away_score"
  colnames(df_filtered)[2] <- "away_team"
  colnames(df_filtered)[3] <- "home_score"
  colnames(df_filtered)[4] <- "home_team"
  # Reorder columns
  df_filtered <- df_filtered[, c(4,3, 2, 1 )]
  df_filtered$away_team <- gsub("\\s*\\(#[0-9]+\\)\\s*", " ", df_filtered$away_team)
  df_filtered$home_team <- gsub("\\s*\\(#[0-9]+\\)\\s*", " ", df_filtered$home_team)
  df_filtered$game_date <- paste0("4/",day,"/24")

  #print(df_filtered)
  apr_future_game_data <- rbind(apr_future_game_data,df_filtered)
}
```

# Merge data into future games
```{r}
# Assuming you have a date column in elo_plot dataframe named "date"

# Load the dplyr package
library(dplyr)

# Arrange elo_plot by team and date
dummy_elo <- elo_plot %>%
  arrange(team, desc(game_date))

# Group by team and select the last Elo score for each team
last_elo <- dummy_elo %>%
  group_by(team) %>%
  slice(1) %>%
  ungroup()

# Rename the columns to match the names in apr_future_games
names(last_elo)[3] <- "home_team"
names(last_elo)[2] <- "last_elo"

# Merge last_elo with apr_future_games based on home_team
apr_future_game_data <- merge(apr_future_game_data, last_elo, by.x = "home_team", by.y = "home_team", all.x = F,all.y = F)

# Rename the last_elo column to home_elo
names(apr_future_game_data)[which(names(apr_future_game_data) == "last_elo")] <- "home_elo"
apr_future_game_data <- subset(apr_future_game_data, select = -c(game_date.y, season_day))
names(apr_future_game_data)[which(names(apr_future_game_data) == "game_date.x")] <- "game_date"
names(apr_future_game_data)[which(names(apr_future_game_data) == "conference")] <- "home_conference"

# Merge last_elo with apr_future_games based on away_team
apr_future_game_data <- merge(apr_future_game_data, last_elo, by.x = "away_team", by.y = "home_team", all.x = F,all.y = F)

# Rename the last_elo column to away_elo
names(apr_future_game_data)[which(names(apr_future_game_data) == "last_elo")] <- "away_elo"
apr_future_game_data <- subset(apr_future_game_data, select = -c(game_date.y, season_day))
names(apr_future_game_data)[which(names(apr_future_game_data) == "game_date.x")] <- "game_date"
names(apr_future_game_data)[which(names(apr_future_game_data) == "conference")] <- "away_conference"
# Print the result
```

# Calculate Win Probabilities for remaining games
```{r}
apr_future_game_data <- apr_future_game_data %>%
  mutate(home_win_prob = prob_win(home_elo,away_elo))
apr_future_game_data$away_win_prob <- 1-apr_future_game_data$home_win_prob
```

# SWAC Remaining Games
```{r}
swac_remaining_games <- apr_future_game_data %>% filter(home_conference =="SWAC"|away_conference == "SWAC")
```


